An Evaluation of RDF Constraint Types to Validate Metadata on Person-Level and Aggregated Data

### 2015-03-12 paper/paper7/paper7-evaluation.tex
evaluation

\begin{document}
\renewcommand{\arraystretch}{1.3}
%
%
\title{RDF Constraint Types to Validate Metadata \\ on Highly-Complex Person-Level and Aggregated Data}
\subtitle{}

@@

Bosch and Eckert initiated a comprehensive database\footnote{Publicly available at \url{http://purl.org/net/rdf-validation}.} on RDF validation requirements to collect case studies, use cases, and requirements \cite{BoschEckert2014}. 
It is continuously updated and used to evaluate and to compare various existing solutions for RDF constraint formulation and validation. 
Requirements are classified to provide a high-level view on different solutions and to facilitate a better understanding of the problem domain.
Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages) \cite{BoschNolleAcarEckert2015}.
We state at least one Disco constraint for the majority of the constraint types.
Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.
When constraint types are mapped to DL, we do not state namespace prefixes for simplicity reasons.

\section{Validation Types}

\textbf{Content-Driven Validation / Data Model Consistency}.
Is the data consistent with the intended semantics of the data model?
Such validation rules ensure the integrity of the data according to the data model.

\textbf{Technology-Driven Validation}.
Some validation rules can be generated automatically out of the defined data model, such as cardinality restrictions, universal quantifications, domains, ranges.

\section{Validation of Metadata on Person-Level and Aggregated Data}

\begin{itemize}
  \item Constraint types marked with an asterisk (*) can be used as OWL 2 axioms. Thus, reasoners may be used to infer implicit triples resolving constraint violations caused when these constraints are validated.
	\item \underline{Underlined subsections} are data model specific constraint types and do not correspond to RDF validation requirements (constraint types).
%	\item \underline{Underlined constraints} are part of content-driven validation.
%	\item \udash{Dashed underlined constraints} are part of technology-driven validation.
\end{itemize}

\subsection{\underline{Comparison}}

\begin{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-01}}: 
	are compared variables represented in a compatible way, i.e. are the variables' code lists theoretically comparable?
		\begin{itemize}
		\item severity level: WARNING
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-02}}: 
	are variable definitions (\emph{dcterms:description}) available for each variable (\emph{disco:Variable}) to compare?
		\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-03}}:
	are code lists structured properly for each variable (\emph{disco:Variable}) to compare?
		\begin{itemize}
		\item severity level: WARNING
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-04}}:
	is for each code (for each variable (\emph{disco:Variable}) to compare) an associated category (a human-readable label) specified?
		\begin{itemize}
		\item severity level: INFO
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-05}}:
	each (\emph{disco:Variable}) to compare must be present.
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\subsection{\underline{Data Model Consistency}}
Is the data consistent with the intended semantics of the data model?
Such validation rules ensure the integrity of the data according to the data model.

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-01:}}
	Only attributes may be optional (\emph{IC-6} \cite{CyganiakReynolds2014}) - 
	The only components of a \emph{qb:DataStructureDefinition} that may be marked as optional, using \emph{qb:componentRequired} are attributes. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-02:}}
	No duplicate observations (\emph{IC-12} \cite{CyganiakReynolds2014}) - 
	No two \emph{qb:Observations} in the same \emph{qb:DataSet} may have the same value for all dimensions. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-03:}}
	Slice Keys consistent with DSD (\emph{IC-8} \cite{CyganiakReynolds2014}) -
	Every \emph{qb:componentProperty} on a \emph{qb:SliceKey} must also be declared as a \emph{qb:component} of the associated \emph{qb:DataStructureDefinition}. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-04:}}
	Required attributes (\emph{IC-13} \cite{CyganiakReynolds2014}) -
	Every \emph{qb:Observation} has a value for each declared attribute that is marked as required. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05:}}
	All measures present (\emph{IC-14} \cite{CyganiakReynolds2014}) -
	In a \emph{qb:DataSet} which does not use a Measure dimension then each individual \emph{qb:Observation} must have a value for every declared measure. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-06:}}
	Measure dimension consistent (\emph{IC-15} \cite{CyganiakReynolds2014}) -
	In a \emph{qb:DataSet} which uses a Measure dimension then each qb:Observation must have a value for the measure corresponding to its given \emph{qb:measureType}. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-07:}}
	Single measure on measure dimension observation (\emph{IC-16} \cite{CyganiakReynolds2014}) -
	In a \emph{qb:DataSet} which uses a Measure dimension then each \emph{qb:Observation} must only have a value for one measure (by \emph{IC-15} this will be the measure corresponding to its \emph{qb:measureType}). 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-08:}}
	All measures present in measures dimension cube (\emph{IC-17} \cite{CyganiakReynolds2014}) -
	In a \emph{qb:DataSet} which uses a Measure dimension then if there is a Observation for some combination of non-measure dimensions then there must be other Observations with the same non-measure dimension values for each of the declared measures. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-09:}}
	Consistent data set links (\emph{IC-18} \cite{CyganiakReynolds2014}) -
	If a \emph{qb:DataSet} \emph{D} has a \emph{qb:slice} \emph{S}, and \emph{S} has an \emph{qb:observation} \emph{O}, then the \emph{qb:dataSet} corresponding to \emph{O} must be \emph{D}. 
\end{itemize}

\begin{itemize}

	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-01\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Relation Clashes}:}}
	Relation Clashes:
  Covers condition S27 from the SKOS reference document, that has not been defined formally. 
	\begin{itemize}
	  \item Implementation:
		In a first step, all pairs of concepts are found that are associatively connected, using a SPARQL query. In the second step, a graph is created, containing only hierarchically related concepts and the respective relations. For each concept pair from the first step, we check for a path in the graph from step two. If such a path is found, a clash has been identified and the causing concepts are returned. 
		\item Severity level: 
	\end{itemize}

	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Clashes}:}}
	Mapping Clashes:
  Covers condition S46 from the SKOS reference document, that has not been defined formally. 
	\begin{itemize}
	  \item Implementation:
		Can be solved by issuing a SPARQL query. 
		\item Severity level: 
	\end{itemize}

	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-03\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Relations Misuse}:}}
	Mapping Relations Misuse:
  According to the SKOS reference documentation, mapping relations (e.g., \emph{skos:broadMatch} or \emph{skos:relatedMatch}) should be asserted to concepts being members of different concept schemes. This check finds concepts that are related by a mapping property and are either members of the same concept scheme or members of no concept scheme at all. 
	\begin{itemize}
		\item Severity level: 
	\end{itemize}

\end{itemize}

\subsection{Subsumption*}

A \emph{subclass axiom}\footnote{{\em R-100-SUBSUMPTION}} ({\em concept inclusion} in DL) states that the class \emph{C1} is a subclass of the class \emph{C2} - \emph{C1} is more specific than \emph{C2}, 
i.e. each resource of the class \emph{C1} must also be part of the class extension of \emph{C2}.

\begin{itemize}
	\item \textbf{{\em DISCO-C-SUBSUMPTION-01:}} 
All {\em disco:Universe}s must also be {\em skos:Concept}s (\ms{Universe $\sqsubseteq$ Concept}).
\end{itemize}

\subsection{Class Equivalence*}

{\em Class Equivalence}\footnote{{\em R-3-EQUIVALENT-CLASSES}} asserts that two concepts have the same instances.
While synonyms are an obvious example of equivalent concepts, in practice one more
often uses concept equivalence to give a name to complex expressions \cite{Kroetzsch2012}.
Concept equivalence is indeed subsumption from left and right ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$).

\begin{itemize}
	\item \textbf{{\em DISCO-C-CLASS-EQUIVALENCE-01:}}
All {\em sio:SIO\_000367} resources must also be {\em disco:Variable}s (\ms{Variable $\equiv$ SIO\_000367}).
The Semanticscience Integrated Ontology (SIO)\footnote{https://code.google.com/p/semanticscience/wiki/SIO} provides a simple, integrated ontology of types and relations for rich description of objects, processes and their attributes.
{\em sio:SIO\_000367} is a variable defined as a value that may change within the scope of a given problem or set of operations.
Thus, {\em sio:SIO\_000367} is equivalent to {\em disco:Variable}.
\end{itemize}

\subsection{Sub Properties*}

{\em Sub Properties}\footnote{\emph{R-54-SUB-OBJECT-PROPERTIES}, \emph{R-64-SUB-DATA-PROPERTIES}} state that the property \emph{P1} is a sub property of the property \emph{P2} - that is, if an individual \emph{x} is connected by \emph{P1} to an individual or a literal \emph{y}, then \emph{x} is also connected by \emph{P2} to \emph{y}.

\begin{itemize}
	\item \textbf{{\em DISCO-C-SUB-PROPERTIES-01:}}
If an individual \emph{x} is connected by {\em disco:fundedBy} to an individual \emph{y}, then \emph{x} is also connected by {\em dcterms:contributor} to \emph{y} (\ms{fundedBy $\sqsubseteq$ contributor}). 
\end{itemize}

\subsection{Property Domains*}

{\em Property Domains}\footnote{{\em R-25-OBJECT-PROPERTY-DOMAIN}, {\em R-26-DATA-PROPERTY-DOMAIN}} ({\em domain restrictions on roles} in DL) restrict the domain of object and data properties.
The purpose is to declare that a given property is associated with a class. 
In OO terms this is the declaration of a member, field, attribute or association. 
$\exists R. \top \sqsubseteq C$ is the object property restriction where $R$ is the object property (role) whose domain is restricted to concept $C$.

\begin{itemize}
	\item \textbf{{\em DISCO-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{Disco} object and data property.
  Only {\em disco:Question}s, e.g., can have {\em disco:responseDomain} relationships (\ms{$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{Data Cube} object and data property.
  Only {\em qb:Observation}s, e.g., can have {\em qb:dataSet} relationships (\ms{$\exists$ dataSet.$\top$ $\sqsubseteq$ Observation}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{DCAT} object and data property.
  Only {\em dcat:Catalog}s, e.g., can have {\em dcat:dataset} relationships (\ms{$\exists$ dataset.$\top$ $\sqsubseteq$ Catalog}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{PHDD} object and data property.
  Only {\em phdd:Table}s, e.g., can have {\em phdd:isStructuredBy} relationships (\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em SKOS-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{SKOS} object and data property.
	Only {\em skos:ConceptSchemes}, e.g., can have {\em skos:hasTopConcept} relationships (\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em XKOS-C-PROPERTY-DOMAIN-01:}} 
	{\em Property Domain} constraints are defined for each \emph{XKOS} object and data property.
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\subsection{Property Ranges*}

{\em Property Ranges}\footnote{{\em R-28-OBJECT-PROPERTY-RANGE}, {\em R-35-DATA-PROPERTY-RANGE}} ({\em range restrictions on roles} in DL) restrict the range of object and data properties.
$\top \sqsubseteq \forall R . C$ is the range restriction to the object property $R$ (restricted by the concept $C$).

\begin{itemize}
	\item \textbf{{\em DISCO-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{Disco} object and data property.
  {\em disco:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{Data Cube} object and data property.
  {\em qb:order} relationships, e.g., can only point to literals of the datatype {\em xsd:string} (\ms{$\top$ $\sqsubseteq$ $\forall$ order.string}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{DCAT} object and data property.
  {\em dcat:bytes} relationships, e.g., can only point to literals of the datatype {\em xsd:integer} (\ms{$\top$ $\sqsubseteq$ $\forall$ bytes.integer}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{PHDD} object and data property.
  {\em phdd:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em SKOS-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{SKOS} object and data property.
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em XKOS-C-PROPERTY-RANGES-01:}} 
	{\em Property Range} constraints are defined for each \emph{XKOS} object and data property.
  {\em xkos:belongsTo} relationships, e.g., can only point to instances of the class {\em skos:Concept} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
	\begin{itemize}
		\item Severity level: ERROR
	\end{itemize}
\end{itemize}

\subsection{Inverse Object Properties*}

In many cases, properties are used bi-directionally and then accessed in the inverse direction, e.g. parent $\equiv$ child$^{-}$. There should be a way to declare value type, cardinality etc of those inverse relations without having to declare a new property URI. 
The object property \emph{OP1} is an inverse\footnote{\emph{R-56-INVERSE-OBJECT-PROPERTIES}} of the object property \emph{OP2}. 
Thus, if an individual \emph{x} is connected by \emph{OP1} to an individual \emph{y}, then \emph{y} is also connected by \emph{OP2} to \emph{x}, and vice versa.

\begin{itemize}
	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-01}}:
	\emph{disco:CategoryStatistics} resources are accessed from codes (\emph{skos:Concept}s) via \emph{disco:statisticsCategory}$^{-}$.
	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-02}}:
	\emph{disco:SummaryStatistics} resources are accessed from \emph{disco:Variable}s via \emph{disco:statisticsVariable}$^{-}$.
	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-03}}:
	\emph{disco:Variable}s are accessed from \emph{disco:Question}s via \emph{disco:question}$^{-}$.
\end{itemize}

\subsection{Symmetric Object Properties*}

A role is symmetric if it is equivalent to its own inverse \cite{Kroetzsch2012}.
An object property symmetry axiom\footnote{\emph{R-61-SYMMETRIC-OBJECT-PROPERTIES}} states that the object property expression \emph{OPE} is symmetric - that is, if an individual \emph{x} is connected by \emph{OPE} to an individual \emph{y}, then \emph{y} is also connected by \emph{OPE} to \emph{x}.

\subsection{Asymmetric Object Properties*}

A property is asymmetric\footnote{{\em R-62-ASYMMETRIC-OBJECT-PROPERTIES}} if it is disjoint from its own inverse \cite{Kroetzsch2012}.
An object property asymmetry axiom states that the object property \emph{OP} is asymmetric - that is, if an individual \emph{x} is connected by \emph{OP} to an individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.

\begin{itemize}
	\item \textbf{{\em DISCO-C-ASYMMETRIC-OBJECT-PROPERTIES-01:}} 
A {\em disco:Variable} may be based on a {\em disco:RepresentedVariable}.
A {\em disco:RepresentedVariable}, however, cannot be based on a {\em disco:Variable}.
This is a kind of mistake which may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}) (\ms{$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$}).
\end{itemize}

\subsection{Reflexive Object Properties*}

\emph{Reflexive Object Properties}\footnote{\emph{R-59-REFLEXIVE-OBJECT-PROPERTIES}} (\emph{reflexive roles}, \emph{global reflexivity} in DL) can be expressed by imposing local reflexivity on the top concept \cite{Kroetzsch2012}.

\subsection{Irreflexive Object Properties*}

An object property is irreflexive\footnote{\emph{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}} (\emph{irreflexive role} in DL) if it is never locally reflexive \cite{Kroetzsch2012}.
An object property irreflexivity axiom \emph{IrreflexiveObjectProperty( OPE )} states that the object property expression \emph{OPE} is irreflexive - that is, no individual is connected by \emph{OPE} to itself.

\begin{itemize}
  \item \textbf{{\em DISCO-C-IRREFLEXIVE-OBJECT-PROPERTIES-01:}}
	In \emph{Disco}, every object property is irreflexive.
  No individual is connected by the object property {\em instrument} to itself (\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists  instrument . Self$}).
\end{itemize}

\subsection{Class-Specific Irreflexive Object Properties*}

A property is \emph{irreflexive} if it is never locally reflexive \cite{Kroetzsch2012}.
An object property irreflexivity axiom states that the object property \emph{OP} is irreflexive - that is, no individual is connected by \emph{OP} to itself.
\emph{Class-Specific Irreflexive Object Properties} are object properties which are irreflexive within a given context, e.g. a class.

\begin{itemize}
  \item \textbf{{\em DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-01:}}
Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves (\ms{Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self.}). 
	\item \textbf{{\em DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-02:}}
Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves (\ms{Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self.}). 
\end{itemize}

\subsection{Disjoint Properties}

A \emph{disjoint properties axiom}\footnote{\emph{R-9-DISJOINT-PROPERTIES}} states that all of the properties are pairwise disjoint; 
that is, no individual \emph{x} can be connected to an individual/literal \emph{y} by these properties.

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{Data Cube} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
  The properties \emph{qb:dataSet} and \emph{qb:structure} are disjoint ($dataSet \sqsubseteq \neg structure$).
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{DCAT} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DISCO-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{Disco} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
  The properties \emph{disco:variable} and \emph{disco:question} are disjoint ($variable \sqsubseteq \neg question$).
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{PHDD} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
	The properties \emph{phdd:isStructuredBy} and \emph{phdd:column} are disjoint ($isStructuredBy \sqsubseteq \neg column$)
\end{itemize}

\begin{itemize}

	\item \textbf{{\em SKOS-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{SKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.

	\item \textbf{{\em SKOS-C-DISJOINT-PROPERTIES-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Disjoint Labels Violation}:}}
	Disjoint Labels Violation:
  Covers condition S13 from the SKOS reference document stating that "\emph{skos:prefLabel}, \emph{skos:altLabel} and \emph{skos:hiddenLabel} are pairwise disjoint properties". 
	\begin{itemize}
	  \item Implementation:
		A SPARQL query collects all labels of all concepts, building an in-memory structure. This structure is then checked for disjoint entries. 
		\item Severity level: 
	\end{itemize}

\end{itemize}

\begin{itemize}
	\item \textbf{{\em XKOS-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{XKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
\end{itemize}

\subsection{Disjoint Classes}

{\em Disjoint Classes}\footnote{{\em R-7-DISJOINT-CLASSES}} state that all of the classes are pairwise disjoint; 
that is, no individual can be at the same time an instance of these disjoint classes.

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-DISJOINT-CLASSES-01:}} 
All \emph{Data Cube} classes are defined to be pairwise disjoint.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-DISJOINT-CLASSES-01:}} 
All \emph{DCAT} classes are defined to be pairwise disjoint.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DISCO-C-DISJOINT-CLASSES-01:}} 
All \emph{Disco} classes are defined to be pairwise disjoint (e.g. \ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}).
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-DISJOINT-CLASSES-01:}} 
All \emph{PHDD} classes are defined to be pairwise disjoint.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em SKOS-C-DISJOINT-CLASSES-01:}} 
All \emph{SKOS} classes are defined to be pairwise disjoint.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em XKOS-C-DISJOINT-CLASSES-01:}} 
All \emph{XKOS} classes are defined to be pairwise disjoint.
\end{itemize}

\subsection{Context-Specific Property Groups}

The \emph{Context-Specific Property Groups}\footnote{\emph{R-66-PROPERTY-GROUPS}} constraint groups data and object properties within a context (e.g. a class).

\subsection{Context-Specific Inclusive OR of Properties}

\emph{Inclusive or} is a logical connective joining two or more predicates that yields the logical value "true" when at least one of the predicates is true.
\emph{Context-Specific Inclusive OR of Properties}\footnote{\emph{R-202-CONTEXT-SPECIFIC-INCLUSIVE-OR-OF-PROPERTIES}} constraints specify that individuals are valid if they have at least one property relationship of one or multiple properties stated within a given context.
The context can be an application profile, a shape, or a class, i.e., the constraint applies for individuals of this specific class.

\subsection{Context-Specific Inclusive OR of Property Groups}

At least one property group must match for individuals of a specific context. 
Context may be a class, a shape, or an application profile.

\subsection{Recursive Queries}

Resource Shapes is a recursive language\footnote{\emph{R-222-RECURSIVE-QUERIES}} (the value shape of a Resource Shape is in turn another Resource Shape). 
There is no way to express that in SPARQL without hand-waving "and then you call the function again here" or "and then you embed this operation here" text.  
The embedding trick doesn't work
in the general case because SPARQL can't express recursive queries,
e.g. "test that this Issue is valid and all of the Issues that references, recursively".
Most SPARQL engines already have
functions that go beyond the official SPARQL 1.1 spec. 
The cost of that sounds manageable.

\subsection{Individual Inequality}

An \emph{individual inequality axiom}\footnote{\emph{R-14-DISJOINT-INDIVIDUALS}} DifferentIndividuals( a$_1$ ... a$_n$ ) states that all of the individuals a$_i$, 1 $\leq$ i $\leq$ n, are different from each other; 
that is, no individuals a$_i$ and a$_j$ with i $\neq$ j can be derived to be equal. 
This axiom can be used to axiomatize the unique name assumption — the assumption that all different individual names denote different individuals.

\subsection{Equivalent Properties*}

An \emph{equivalent object properties axiom}\footnote{\emph{R-4-EQUIVALENT-OBJECT-PROPERTIES}} \emph{EquivalentObjectProperties( OPE$_1$ ... OPE$_n$ )} states that all of the object property expressions \emph{OPE$_i$, 1 $\leq$ i $\leq$ n}, are semantically equivalent to each other. This axiom allows one to use each \emph{OPE$_i$} as a synonym for each \emph{OPE$_j$} — that is, in any expression in the ontology containing such an axiom, \emph{OPE$_i$} can be replaced with \emph{OPE$_j$} without affecting the meaning of the ontology. The axiom \emph{EquivalentObjectProperties( OPE$_1$ OPE$_2$ )} is equivalent to the following two axioms \emph{SubObjectPropertyOf( OPE$_1$ OPE$_2$ )} and \emph{SubObjectPropertyOf( OPE$_1$ OPE$_2$ )}.

An \emph{equivalent data properties axiom}\footnote{\emph{R-5-EQUIVALENT-DATA-PROPERTIES}} \emph{EquivalentDataProperties( DPE$_1$ ... DPE$_n$ )} states that all the data property expressions \emph{DPE$_i$, 1 $\leq$ i $\leq$ n}, are semantically equivalent to each other. This axiom allows one to use each \emph{DPE$_i$} as a synonym for each \emph{DPE$_j$} — that is, in any expression in the ontology containing such an axiom, DPE$_i$ can be replaced with \emph{DPE$_j$} without affecting the meaning of the ontology. The axiom \emph{EquivalentDataProperties( DPE$_1$ DPE$_2$ )} can be seen as a syntactic shortcut for the following axiom \emph{SubDataPropertyOf( DPE$_1$ DPE$_2$ )} and \emph{SubDataPropertyOf( DPE$_1$ DPE$_2$ )}.

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-EQUIVALENT-PROPERTIES-01:}}
	Equivalent properties from different versions of \emph{Data Cube} can be marked as equivalent. 
	As a consequence, the properties can be replaced by each other without affecting the meaning.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-EQUIVALENT-PROPERTIES-01:}}
	Equivalent properties from different versions of \emph{DCAT} can be marked as equivalent. 
	As a consequence, the properties can be replaced by each other without affecting the meaning.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DISCO-C-EQUIVALENT-PROPERTIES-01:}}
	Equivalent properties from different versions of \emph{Disco} can be marked as equivalent, e.g. \emph{disco:containsVariable} and \emph{disco:variable}. 
	As a consequence, the properties can be replaced by each other without affecting the meaning.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-EQUIVALENT-PROPERTIES-01:}}
	Equivalent properties from different versions of \emph{PHDD} can be marked as equivalent. 
	As a consequence, the properties can be replaced by each other without affecting the meaning.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em SKOS-C-EQUIVALENT-PROPERTIES-01:}}
	Equivalent properties from different versions of \emph{SKOS} can be marked as equivalent. 
	As a consequence, the properties can be replaced by each other without affecting the meaning.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em XKOS-C-EQUIVALENT-PROPERTIES-01:}}
	Equivalent properties from different versions of \emph{XKOS} can be marked as equivalent. 
	As a consequence, the properties can be replaced by each other without affecting the meaning.
\end{itemize}

\subsection{Property Assertions}

\emph{{Property Assertions}}\footnote{\emph{R-96-PROPERTY-ASSERTIONS}}
and includes positive property assertions and negative property assertions.
A \emph{positive object property assertion ObjectPropertyAssertion( OPE a$_1$ a$_2$ )} states that the individual a$_1$ is connected by the object property expression \emph{OPE} to the individual a$_2$. 
A \emph{negative object property assertion NegativeObjectPropertyAssertion( OPE a$_1$ a$_2$ )} states that the individual a$_1$ is not connected by the object property expression \emph{OPE} to the individual a$_2$. 
A \emph{positive data property assertion DataPropertyAssertion( DPE a lt )} states that the individual a is connected by the data property expression DPE to the literal \emph{lt}. 
A \emph{negative data property assertion NegativeDataPropertyAssertion( DPE a lt )} states that the individual a is not connected by the data property expression \emph{DPE} to the literal \emph{lt}.

\subsection{Data Property Facets}

For datatype properties it should be possible to declare frequently needed \emph{facets}\footnote{\emph{R-46-CONSTRAINING-FACETS}} to drive user interfaces and validate input against simple conditions, including min/max value, regular expressions, string length - similar to XSD datatypes. 
Constraining facets, to restrict datatypes of RDF literals, may be: \emph{xsd:length}, \emph{xsd:minLength}, \emph{xsd:maxLength}, \emph{xsd:pattern}, \emph{xsd:enumeration}, \emph{xsd:whiteSpace}, \\ \emph{xsd:maxInclusive}, \emph{xsd:maxExclusive}, \emph{xsd:minExclusive}, \emph{xsd:minInclusive}, \emph{xsd:total} \emph{Digits}, \emph{xsd:fractionDigits}.

\begin{itemize}
	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-01:}} The abstract of a study (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minLength}) of x. 
\end{itemize}

\subsection{Literal Pattern Matching}

There are multiple use cases associated with the requirement to match literals according to given patterns\footnote{\emph{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}.

\begin{itemize}
	\item \textbf{{\em DISCO-C-LITERAL-PATTERN-MATCHING-01:}} Each \emph{disco:Variable} of a given \emph{disco:LogicalDataSet} must have a given prefix for its variable name (\emph{skos:notation}). 
\end{itemize}

\subsection{Negative Literal Pattern Matching}

Literals of given data properties within given contexts do not have to match given patterns\footnote{\emph{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}.

\begin{itemize}
	\item \textbf{{\em DISCO-C-NEGATIVE-LITERAL-PATTERN-MATCHING-01:}} 
\end{itemize}

\subsection{Object Property Paths*}

\emph{Object Property Paths}\footnote{\emph{R-55-OBJECT-PROPERTY-PATHS}} (or \emph{Object Property Chains} and in DL terminology \emph{complex role inclusion axiom} or \emph{role composition}) is the more complex form of sub properties. 
This axiom states that, if an individual \emph{x} is connected by a sequence of object property expressions \emph{OPE$_1$, ..., OPE$_n$} with an individual \emph{y}, then \emph{x} is also connected with \emph{y} by the object property expression \emph{OPE}.  
Role composition can only appear on the left-hand side of complex role inclusions \cite{Kroetzsch2012}.

\subsection{Intersection*}

>>>>

\begin{document}
\renewcommand{\arraystretch}{1.3}
%
%
\title{An Evaluation of RDF Constraint Types to Validate Metadata on Person-Level and Aggregated Data}
\subtitle{}

@@

\section{Data Cube}

\begin{itemize}
	\item \url{http://270a.info/} (see the VoID which points to other
VoIDs) is full of data sets (probably close to 10k) using RDF Data Cube,
and some of those also include XKOS.
\end{itemize}
